Title Goes Here

### 2024-05-13 analysis/paper/paper.qmd
EEO

>>>>

```{r}
# EEO
library(stringr)
library(dplyr)
library(stopwords)
library(tidyverse)
library(tm)

stopwords <- stopwords("en")

EEO <- jobdata %>%
  select(equal_employment_opportunity_statement)

remove_stopwords <- function(text, stopwords) {
  pattern <- paste0("\\b(", paste(stopwords, collapse = "|"), ")\\b")
  str_remove_all(text, pattern)
}

EEO_wordcount <- EEO %>%
  mutate(word_count = str_count(equal_employment_opportunity_statement, "\\S+")) %>%
  print()

EEO_clean <- EEO %>%
  mutate(equal_employment_opportunity_statement = str_to_lower(equal_employment_opportunity_statement), 
         equal_employment_opportunity_statement = str_remove_all(equal_employment_opportunity_statement, "[[:punct:]]"),
         equal_employment_opportunity_statement = remove_stopwords(equal_employment_opportunity_statement, stopwords))

EEO_word <- EEO_clean %>%
   unnest_tokens(word, text) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)
```

```{r}
ggplot(word_data, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  coord_flip() +  # Flips the axes for easier reading of text
  labs(x = "Words", y = "Frequency", title = "Word Frequency")
```
